Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-24 manuscript/draft.Rmd
minor edit for #4

Many ecological forecasts use data that is readily available and easy to work
with. While ease of use is a reasonable consideration it is also important to
include predictor variables that are expected to relate to the ecological
quantity being forecast and dynamic time-series of predictors instead of
long-term averages. Investing time in identifying and acquiring better predictor
variables may have at least as many benefits as using more sophisticated
modeling techniques [@kent2014].

>>>>

Many ecological forecasts use data that is readily available and easy to work
with. While ease of use is a reasonable consideration it is also important to
include predictor variables that are expected to relate to the ecological
quantity being forecast. Time-series of predictors, instead of long-term
averages, are also preferable to match the ecologial data (see #2).
Investing time in identifying and acquiring better predictor
variables may have at least as many benefits as using more sophisticated
modeling techniques [@kent2014].
